### 2021-06-07 paper/report.tex
Add some first comments.

Susceptibility to contracting the SARS-CoV-2 virus is dependent on age; so is the
progression of a possible infection. We differentiate between an inital period of
infection without being infectious or showing symptoms, being infectious (presymptomatic
or asymptomatic), showing symptoms, requiring intensive care, and recovery or death. The
probabilities of transitioning between these states depend on age; their duration is
random within intervals calibrated to medical literature.\comment[id=HM]{Cite}.
Conditional on the type of contact, infectiousness independent of ages \citep{Jones2021}.

The model includes several other features, which are crucial to describe the evolution of
the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness and disease progress can be introduced. With a probability calibrated to
XXX\comment[id=HM]{Klara, please add citatiion}, vaccinated agents become immune and they
do not transmit the virus. While vaccines are rolled out, priority may depend on age and
occupation. Agents may demand two types of tests as described in
Figure~\ref{fig:pcr_antigen_tests}. First, polymerase chain reaction (PCR) tests directly
reveal whether an individual is infected or not. PCR tests require some time to be
processed and there are always aggregate capacity constraints. Second, rapid antigen
tests yield immediate results. Specificity and sensitivity of these tests is set
according to the XXX data.\comment[id=HM]{subsequent PCR tests, quarantine, work/school}.
Demand for rapid tests will depend on policy, e.g., prices, testing requirements before
work, attending school, or visiting restaurants and shops.

>>>>

Susceptibility to contracting the SARS-CoV-2 virus is dependent on age; so is the
progression of a possible infection. We differentiate between an initial period of
infection without being infectious or showing symptoms, being infectious (presymptomatic
or asymptomatic), showing symptoms, requiring intensive care, and recovery or death. The
probabilities of transitioning between these states depend on age; their duration is
random within intervals calibrated to medical literature (for a detailed description see
Section~\ref{sec:medical_params}).
Conditional on the type of contact, infectiousness independent of ages \citep{Jones2021}.

The model includes several other features, which are crucial to describe the evolution of
the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness and disease progress can be introduced. With a probability calibrated to
\cite{Hunter2021}, vaccinated agents become immune and they do not
transmit the virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.
% the sources only report reduced viral shedding and reduced risk of infection.
% Lauterbach calculated that taking the risk of infection * reduced infectiousness given
% infection based on theses studies suggest that given exposure the risk that fully
% vaccinated individuals pose is <10% of an unvaccinated person.
While vaccines are rolled out, priority may depend on age and occupation. Agents may
demand two types of tests as described in Figure~\ref{fig:pcr_antigen_tests}. First,
polymerase chain reaction (PCR) tests directly reveal whether an individual is infected
or not. PCR tests require some time to be processed and there are always aggregate
capacity constraints. Second, rapid antigen tests yield immediate results. Specificity
and sensitivity of these tests is set according to data by \cite{Bruemmer2021, Smith2021}
. The sensitivity of the rapid antigen tests depends on the timing of the test relative
to the start of infectiousness.\comment[id=HM]{subsequent PCR tests, quarantine,
work/school}. Demand for rapid tests will depend on policy, e.g., prices, testing
requirements before work, attending school, or visiting restaurants and shops.
